Predicting Success of Motivational Interviews with Recurrent Neural Network and Probabilistic Model for Patient-Provider Communication Sequences

### 2017-09-09 paper-amia-summit-2018/amia_summit_2018.tex
update word embedding part of the paper

\textbf {MYSCOPE code embedding}: We utilize word embedding in place of one-hot vectors for the representation of behavior code. Because one-hot vectors are high-dimensional and sparse. On the other hand, word embeddings have the ability to represent semantically similar words with similar vectors in a lower dimensional space by retaining their internal relations. Figure~\ref{fig:code_embedding} illustrates the myscope code embedding visualize with t-SNE, a sophisticated technique for visualizing high-dimensional data. It can be seen that similar behavior codes are placed close to each other in high dimensional vector space such as OQECHT+, OQECML+, AF, ADV+, RCML+S, etc are nearest neighbors of CQECML+, which make sense in real world practice.   
\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.50\textwidth]{figures/code_embed.eps}
    \caption{\textbf{T-SNE diagram of behavior code drawn after 4000 steps with perplexity 30}.}
    \label{fig:code_embedding}
\end{figure}

>>>>

\textbf {MYSCOPE code embedding}: We utilize word embedding in place of one-hot vectors for the representation of behavior code. Because one-hot vectors are high-dimensional and sparse. On the other hand, word embeddings have the ability to represent semantically similar words with similar vectors in a lower dimensional space by retaining their internal relations. Figure~\ref{fig:code_embedding} illustrates the myscope code embedding visualize with t-SNE, a sophisticated technique for visualizing high-dimensional data. It can be seen that similar behavior codes are placed close to each other in high dimensional vector space such as OQECHT+, OQECML+, AF, ADV+, RCML+S, etc. are nearest neighbors of CQECML+, which make sense in real world practice.   
\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.50\textwidth]{figures/code_embed.eps}
    \caption{\textbf{T-SNE diagram of behavior code drawn after 4000 steps with perplexity 30}.}
    \label{fig:code_embedding}
\end{figure}
